Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

On the one hand, a close-in planet that changes the star's rotation and activity makes it more difficult for us to model the system's evolution, as it affects fundamental stellar parameters. Inferring stellar age from rotation may be biased, if the star is spun up or spun down relative to stars without close-in companions~(XXXX). Analogously, altered activity levels may mimic an older or younger host than it actually is~\citep{ilic2022tidal}.

On the other hand, understanding short-term, magnetic star-planet interactions -- the focus of this work -- holds promise to provide important insights into the habitability of the entire system~(XXXX). Planets involved in such interactions are in-situ probes of the system's space weather~(XXXX), and could prospectively reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.

@@

\subsection{Searching for global changes in actvity}
\label{sec:intro:global}
Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but just a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}. Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive}. In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces selection bias in the activity measure. It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}.

\subsection{Flares}
\label{sec:intro:flares}
In this study, we will look at stellar flares as another way of dissipating the energy deposited in the magnetic field. Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}. In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars up to hundreds of parsecs away~(XXXX). But since they occur randomly in time, individual events can be hard to catch. %We can observe flares in nearly all electromagnetic bands -- from radio to X-ray~\citep{benz2010physical}.

@@

\subsection{Searching for local changes in activity}
\label{sec:intro:local}
Phase correlated activity, flaring and otherwise, has been searched for in individual systems. After eight years of monitoring of HD 189733, an X-ray active Hot Jupiter host, the observed slight clustering of flaring in orbital phase remains tentative~\citep{pillitteri2022xray}. \citet{maggio2015coordinated} observed a flare-up in X-ray when the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156. However, a similar study using chromospheric indicators in the eccentric system HD 80606 found no variation between periastron and apoastron~\citep{figueira2016activity}. In the above cases, non-detection can at least partly be attributed to poor orbital phase coverage, which also limits the significance of any positive detection. Realizing this, \citet{fischer2019timevariable} used K2 data with excellent phase coverage of the orbits of the inner TRAPPIST-1 planets to look for clustered flaring in phase, but found none. Similarly, in \citet{ilin2022searching}, we found hints of excess flaring in the TESS light curves of the young AU Mic system. This mixed picture of individual object studies calls for a more comprehensive and systematic approach.

@@

Based on the filtered PSCP table, we use the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves. In total, we searched 7258 light curves for flares -- 3030 Kepler Quarters, and 4228 TESS Sectors. We found and analyzed light curves for a total of 1811 systems, 344 of which were observed only by the primary Kepler mission, 1205 only by TESS, and 262 by both missions. We did not use K2 light curves because of the many systematics, and consequently the high costs of de-trending them. But we included the flare list obtained by~\citet{paudel2018k2} for TRAPPIST-1 K2 flares, since this system is a potential candidate for sub-Alfv\'enic interactions~\citep{fischer2019timevariable}.

@@

\subsection{Light curve de-trending and flare search}
\label{sec:methods:flaresearch}
To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process. First, we apply a spline fit with a coarse sampling of 30h-averaged values to capture slow rotation with periods above multiple days and non-periodic trends. Then, we iteratively fit a series of sines to capture rotational signal on time scales down to about half a day, close to the fastest rotational signals measured in low mass stars. Eventually, we apply two Savitzky-Golay~\citep{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each. At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for very active stars like AU Mic or Proxima Cen) threshold as flare candidates to prevent the filter from ironing out the flares. As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.

In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level, implemented in AltaiPony~\cite{ilin2021altaipony}. We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars). To capture the exponential tail of the flare, we use the \texttt{addtail} flag in the \texttt{find\_flares} method to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.

@@

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_transiting.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS. The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black. Phase zero corresponds to the transit mid-time of the planet. 
        }
        \label{fig:cumdist_transiting}
    \end{centering}
\end{figure*}

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_rv.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the non-transiting planet hosts observed by Kepler and TESS. The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black. Phase zero is chosen arbitrarily. 
        }
        \label{fig:cumdist_rv}
    \end{centering}
\end{figure*}

\subsection{Flaring star-planet interaction signal}
\label{sec:results:spi}
We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations. We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares with the same energy relative to stellar luminosity. We show the results that include all flares regardless of $ED$ in the appendix (XXXX TBD).

Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system. We do not find any $>3\sigma$ signal of star-planet interaction in our sample. However, overall, the significance of the deviation increases with higher expected power of interaction, which is also listed for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.

@@

\begin{figure*}[ht!]
    \script{paper_adtest_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
        \caption{
            Expected power of SPI vs. AD test results, assuming four different scenarios, color-coded by stellar surface field strength.
        }
        \label{fig:adtest_bp}
    \end{centering}
\end{figure*}

@@

AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}. The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower. If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring. Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation. Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet=induced flaring.
For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.

K2-25 is a multiplanet system around a fast rotating ($<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Moreover, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}. This might at least in part be due to the stellar wind conditions around K2-25 b. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius.

K2-25 is eccentric, see Eike Günther?

In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}. Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}. It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field and closest orbit among the three systems.

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, all systems that do not show elevated interaction, have a weaker magnetic field below $2000\,$G~(top row in Figure\ref{fig:adtest_bp}). In the Alfv\'en wing scenario~(bottom row in Figure\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring. In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit (note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it). All else equal, this is more likely if the stellar magnetic field strength is weaker. Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following Section.

\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2\sigma$ level, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.

HIP 67522 is a young Sun, currently contracting onto the main sequence. It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}. Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$, closer than any other system in our sample. Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet. However, if we calculate the $p$-value of AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$. Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.

@@

\subsubsection{TAP 26}
\label{sec:results:individualstars:tap26}
TAP 26 is a weak-line T-Tauri star with a strong magnetic field~\citep{yu2017hot}. \citet{lanza2018closeby} estimate that the system can release more energy in magnetic star-planet interaction than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}. However, for TAP 26 b, the orbital period might is not well-constrained. \citet{yu2017hot} apply several methods to derive $P_{orb}$ from the radial velocity data: While the $10.8\,$d orbit we adopted is the most likely according to \citet{yu2017hot}, a $9.0\,$d orbit is also likely, and some of their applied methods favored a $13.4\,$d period. The absence of interaction could hence be a consequence of uncertain orbital period. However, intermittent interactions and the viewing geometry of TAP 26 could also explain the absence of phase-correlated flaring~(see Sections~\ref{sec:discussion:intermittency} and \ref{sec:discussion:viewing}).

\subsubsection{KOI-12}
\label{sec:results:individualstars:koi12}
KOI-12, also known as Kepler-448, is a young two-planet system with an eccentric outer planet KOI-12 c, and an inner Hot Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}. With respect to rotation rate, stellar and planetary radius, the KOI-12/KOI-12 b system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence). Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b. Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522. Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.

@@

\section{Discussion}
\label{sec:discussion}
Eccentricity is almost controlled for in our sample~(Section~\ref{sec:discussion:eccentricity}), while rotation is not well enough constrained to investigate the presence of flaring modulation with $P_{rot}$, or the synodic period~(Section~\ref{sec:discussion:rotsyn}). In the remainder of the discussion, we lay out different reasons for the emerging shape of the distribution in our results in Fig.~\ref{fig:adtest_bp}, in particular the inactive and active branches at high expected power of interaction. We begin with the possible intermittency of the interaction that could be caused by the planet regularly moving in and out of the sub-Alfv\'enic zone for extended periods of time~(Section~\ref{sec:discussion:intermittency}). In Section~\ref{sec:discussion:viewing}, we suggest that the absence of interaction at high expected power could be due to unfavorable viewing geometry of the system, e.g., a face-on orbital plane. In Section~\ref{sec:discussion:misalignment}, we discuss whether (mis-)alignment between spin, orbit and magnetic dipole can increase or decrease the chances of flaring star-planet interaction. In Section~\ref{sec:discussion:commensurability}, we note that systems on the inactive branch are further away from spin-orbit commensurability than stars on the active branch. This leads us to conjecture a possible influence of tidal interactions on the occurrence of orbital phase correlated flaring. We conclude our discussion by following this line of reasoning, and consider ways to disentangle tidal from magnetic interactions~(Section~\ref{sec:discussion:tidalmagnetic}).

\subsection{Eccentricity}
\label{sec:discussion:eccentricity}
If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius. If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage. This was previously exploited in the case of HD 189733~(XXXX), and also for binary interaction in the V 773 Tau system~(XXXX). In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$. The exception is K2-25, with a relative high $e=0.45$, which may contribute to the increased contrast of excess flares. All else equal, closer proximity increases the strength of interaction. Perhaps, K2-25 even moves in and out of the sub-Alfv\'enic zone between periastron and apoastron, turning interaction on and off every single orbit. If periastron passage occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further enhanced by the narrow phase range of the periastron passage.

@@

We have conducted the so far largest search for flaring star-planet interactions. Using over 7000 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we found searched for flares in over 1800 systems of the over 3000 listed in the NASA Exoplanet Archive. In those systems that were single stars, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase. Our final sample consisted of 26 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.

>>>>

On the one hand, a close-in planet that changes the star's rotation and activity makes it more difficult for us to model the system's evolution, as it affects fundamental stellar parameters. Inferring stellar age from rotation may be biased, if the star is spun up or spun down relative to stars without close-in companions~\citep{tejadaarevalo2021further, brown2014discrepancies, maxted2015comparison}. Analogously, altered activity levels may mimic an older or younger host than it actually is~\citep{ilic2022tidal}.

On the other hand, understanding short-term, magnetic star-planet interactions -- the focus of this work -- can provide important insights into the habitability of the entire system~\citep{shkolnik2018signatures}. Even if they orbit far inside the habitable, planets involved in such interactions are in-situ probes of the system's space weather and mass loss by revealing the extent of the Alfv\'en zone~\citep{kavanagh2021planetinduced, chebly2022destination}. Prospectively, planet-induced stellar activity could reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.

@@

\subsection{Searching for global changes in actvity}
\label{sec:intro:global}
Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but just a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}. Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive, poppenhaeger2010coronal}. In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces selection bias in the activity measure. It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}. Tidal interactions can also induce global increase in activity~\citep{ilic2022tidal}, which adds further ambiguity to the interpretation.

\subsection{Flares}
\label{sec:intro:flares}
In this study, we will look at stellar flares as another way of dissipating the energy deposited in the magnetic field. Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}. In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars over 1kpc away~\citep{chang2015}. But since they occur randomly in time, individual events can be hard to catch. %We can observe flares in nearly all electromagnetic bands -- from radio to X-ray~\citep{benz2010physical}.

@@

\subsection{Searching for local changes in activity}
\label{sec:intro:local}
Phase-correlated activity, flaring and otherwise, has been searched for in individual systems. After eight years of monitoring of HD 189733, an X-ray active Hot Jupiter host, the observed slight clustering of flaring in orbital phase remains tentative~\citep{pillitteri2022xray}. \citet{maggio2015coordinated} observed an eruption of X-ray emissionwhen the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156. However, a similar study using chromospheric indicators in the eccentric system HD 80606 found no variation between periastron and apoastron~\citep{figueira2016activity}. In the above cases, non-detection can at least partly be attributed to poor orbital phase coverage, which also limits the significance of any positive detection. Realizing this, \citet{fischer2019timevariable} used K2 data with excellent phase coverage of the orbits of the inner TRAPPIST-1 planets to look for clustered flaring in phase, but found none. \citet{ilin2022searching} and \citet{klein2022one} found hints of excess flaring, and chromospheric Helium emission in the young AU Mic system, respectively. This mixed picture of individual object studies calls for a more comprehensive and systematic approach.

@@

Based on the filtered PSCP table, we use the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves. In total, we searched 7258 light curves for flares -- 3030 Kepler Quarters, and 4228 TESS Sectors. We found and analyzed light curves for a total of 1811 systems, 344 of which were observed only by the primary Kepler mission, 1205 only by TESS, and 262 by both missions. We did not use K2 light curves because of the many systematics, and consequently the high time investment of de-trending them. But we included the flare list obtained by~\citet{paudel2018k2} for TRAPPIST-1 K2 flares, since this system is a potential candidate for sub-Alfv\'enic interactions~\citep{fischer2019timevariable}.

@@

\subsection{Light curve de-trending and flare search}
\label{sec:methods:flaresearch}
To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process, implemented as the \texttt{custom\_detrending} method in \texttt{AltaiPony}, a flare science package for light curve analysis~\citep{ilin2021altaipony}. First, we apply a spline fit with a coarse sampling of 30h-averaged values to capture slow rotation with periods above multiple days and non-periodic trends. Then, we iteratively fit a series of sines to capture rotational signal on time scales down to about half a day, close to the fastest rotational signals measured in low mass stars. Eventually, we apply two Savitzky-Golay~\citep{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each. At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for very active stars like AU Mic or Proxima Cen) threshold as flare candidates to prevent the filter from ironing out the flares. As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.

In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level using the \texttt{AltaiPony} method \texttt{find\_flares}. We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars). To capture the exponential tail of the flare, we use the \texttt{addtail} flag in the \texttt{find\_flares} method to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.

@@

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_transiting.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the \textit{transiting} planet hosts observed by Kepler and TESS, sorted by number of flares from top to bottom. The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black. Phase zero corresponds to the transit mid-time of the planet. 
        }
        \label{fig:cumdist_transiting}
    \end{centering}
\end{figure*}

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_rv.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the \textit{non-transiting} planet hosts observed by Kepler and TESS, sorted by number of flares from top to bottom. The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black. Phase zero is chosen arbitrarily. 
        }
        \label{fig:cumdist_rv}
    \end{centering}
\end{figure*}

\subsection{Flaring star-planet interaction signal}
\label{sec:results:spi}
We used the custom Anderson-Darling test introduced in~\citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations. We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares with the same energy relative to stellar luminosity. We show the results that include all flares regardless of $ED$ in the appendix (XXXX TBD).

Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system. There is no star-planet system for which we find a $>3\sigma$ signal of star-planet interaction in our sample. However, overall, the significance of the deviation increases with higher expected power of interaction, which is also listed for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.

@@

\begin{figure*}[ht!]
    \script{paper_adtest_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
        \caption{
            Expected power of SPI vs. AD test results, assuming four different scenarios, color-coded by stellar surface field strength. Top row: Stretch-and-break scenario. Bottom row: Alfv\'en wing scenario. Left column: assuming $B_p=1\,$G. Right column: assuming $B_p=1\,$G. While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
        }
        \label{fig:adtest_bp}
    \end{centering}
\end{figure*}

@@

AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}. The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower. If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring. Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation. Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet-induced flaring.
For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.

K2-25 is a multiplanet system around a fast rotating ($P_{rot}<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}. This might in part be due to the stellar wind conditions around K2-25 b. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).

In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}. Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}. It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field, and closest orbit among the three systems.

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(top row in Figure~\ref{fig:adtest_bp}). In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring. In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit. It is important to note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained. All else equal, this is more likely if the stellar magnetic field strength is weaker. Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two Sections.

\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2\sigma$ level, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.61$ and $\sim 0.81$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.

HIP 67522 is a young Sun, currently contracting onto the main sequence. It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}. Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$. Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet. However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.

@@

\subsubsection{TAP 26}
\label{sec:results:individualstars:tap26}
TAP 26 is a weak-line T-Tauri star with a strong magnetic field~\citep{yu2017hot}. \citet{lanza2018closeby} estimate that the system can release more energy in magnetic star-planet interaction than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}. However, for TAP 26 b, the orbital period might not be well-constrained. \citet{yu2017hot} apply several methods to derive $P_{orb}$ from the radial velocity data: While the $10.8\,$d orbit we adopted is the most likely according to \citet{yu2017hot}, a $9.0\,$d orbit is also likely, and some of their applied methods favored a $13.4\,$d period. The absence of interaction could hence be a consequence of uncertain orbital period. However, intermittent interactions and the viewing geometry of TAP 26 could also explain the absence of phase-correlated flaring~(see Sections~\ref{sec:discussion:intermittency} and \ref{sec:discussion:viewing}).

\subsubsection{KOI-12}
\label{sec:results:individualstars:koi12}
KOI-12, also known as Kepler-448, is a two-planet system with an eccentric outer planet KOI-12 c, and an inner Warm Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}. With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence). In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 subgiant~\citep{frasca2016activity}, which is already evolving off the main sequence. Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b. Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522. Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.

@@

\section{Discussion}
\label{sec:discussion}
Eccentricity is almost controlled for in our sample~(Section~\ref{sec:discussion:eccentricity}), while rotation is not well enough constrained to investigate the presence of flaring modulation with $P_{rot}$, or the synodic period~(Section~\ref{sec:discussion:rotsyn}). In the remainder of the discussion, we lay out different reasons for the emerging shape of the distribution in our results in Fig.~\ref{fig:adtest_bp}, in particular the inactive and active branches at high expected power of interaction. We begin with the possible intermittency of the interaction that could be caused by the planet regularly moving in and out of the sub-Alfv\'enic zone for extended periods of time~(Section~\ref{sec:discussion:intermittency}). In Section~\ref{sec:discussion:viewing}, we suggest that the absence of interaction at high expected power could be due to unfavorable viewing geometry of the system, e.g., a face-on orbital plane. In Section~\ref{sec:discussion:commensurability}, we note that systems on the inactive branch are further away from spin-orbit commensurability than stars on the active branch. This leads us to conjecture a possible link between spin-orbit resonance and flaring SPI.

\subsection{Eccentricity}
\label{sec:discussion:eccentricity}
If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius. If then the apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage. This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}. In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$. The exception is K2-25, with a relatively high $e=0.45$. If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further increased by the narrow phase range of the periastron passage. \citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}). We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity.

@@

We have conducted the so far largest search for flaring star-planet interactions. Using over 7200 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we searched for flares in over 1800 systems of the about 3000 listed in the NASA Exoplanet Archive. In the single star systems, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase. Our final sample consisted of 26 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
